Supplementary Information: Tropical tree drought sensitivity is jointly shaped by drought characteristics, species adaptations, and individual microenvironments

### 2025-04-03 doc/manuscript_hkk_drought_sensitivity.Rmd
updated Fig 1 with code fixed
updated doc with accents to names

ft <- flextable(sumtab)
ft <- set_header_labels(ft,
  na = ""
)
ft <- hline(ft, i = c(1, 4, 7), part = "body")
ft <- line_spacing(ft, space = 1, part = "all")
ft <- autofit(ft)
# ft <- height(ft, height = 0.3)
ft <- bold(ft, i = c(1, 4, 7), bold = TRUE, part = "body")
ft <- width(ft, 1, width = 3.5)
# ft <- width(ft, 2, width = 1.75)
# ft <- width(ft, 3, width = 3)
ft
```

@@

We acknowledge the continued contributions of the Huai Kha Khaeng forest monitoring team in collecting data and maintaining the dendrometer bands. 
Ekaphan Kraichak and Kanisorn Chowtiwuttakorn helped with procuring elevation and climate datasets. 
Jose Medina-Vega, Valentine Herrmann and Eugenie Mas provided input on improving analyses.  
KA was supported by the Smithsonian Institution Postdoctoral Fellowship and the ForestGEO Analytical Workshop, Asia 2024 in completing this work.

>>>>

ft <- flextable(sumtab)
ft <- set_header_labels(ft,
  na = ""
)
ft <- hline(ft, i = c(1, 4, 7), part = "body")
ft <- line_spacing(ft, space = 1, part = "all")
ft <- autofit(ft)
# ft <- height(ft, height = 0.3)
ft <- bold(ft, i = c(1, 4, 7), bold = TRUE, part = "body")
ft <- width(ft, 1, width = 3.5)
# ft <- width(ft, 2, width = 1.75)
# ft <- width(ft, 3, width = 3)
ft <- set_caption(ft, caption = "Summary table of hypotheses tested, effects of variables on drought sensitivity and corresponding evidence")
ft
```

@@

We acknowledge the continued contributions of the Huai Kha Khaeng forest monitoring team in collecting data and maintaining the dendrometer bands. 
Ekaphan Kraichak and Kanisorn Chowtiwuttakorn helped with procuring elevation and climate datasets. 
José Medina-Vega, Valentine Herrmann and Eugenie Más provided input on improving analyses. 
KA was supported by the Smithsonian Institution Postdoctoral Fellowship and the ForestGEO Analytical Workshop, Asia 2024 in completing this work.
